---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
library(dplyr)
library(readr)
library(ggplot2)
library(matrixStats)
library(xtable)
```

# RQ1

## Data

```{r data, include=FALSE}
commons_codec_trials <- read_delim("../../RQ1/data/random_exp/commons-codec-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
commons_collections_trials <- read_delim("../../RQ1/data/random_exp/commons-collections-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
commons_io_trials <- read_delim("../../RQ1/data/random_exp/commons-io-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
commons_lang_trials <- read_delim("../../RQ1/data/random_exp/commons-lang-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
gson_trials <- read_delim("../../RQ1/data/random_exp/gson-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
jgit_trials <- read_delim("../../RQ1/data/random_exp/jgit-trials.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
all_trials <- rbind(commons_codec_trials, commons_collections_trials, commons_io_trials, gson_trials, jgit_trials)

```



## Add

Cleaning up data, Regrouping, etc

```{r pre_add}
transfoBarPlot_tp <- function(data, filter_val,t) {
  all_success <- data %>% filter(status >= 0 & name=="add") %>% group_by(nodeTransplantationPoint) %>% count_()
  all_compile <- data %>% filter(status >= -1 & name=="add") %>% group_by(nodeTransplantationPoint) %>% count_()
  
  r <- merge(all_success,all_compile, by='nodeTransplantationPoint', all=T) 
  
  if(nrow(r[is.na(r$'n.x'),]) > 0) {
    r[is.na(r$'n.x'),]$'n.x' <- 0
  }
  r$sr <- r$'n.x' / r$'n.y'
  
  q <- r %>% filter(n.y > filter_val)
  weightedMedian(q$sr, q$n.y)
  weightedMean(q$sr, q$n.y)
  median(q$sr)
  mean(q$sr)
  sd(q$sr)
  par(mar = c(4, 16, 0, 0)) 
  
  barplot(q$sr,names.arg = q$nodeTransplantationPoint, las = 2, horiz = T, col=c("darkblue"), border = T, main = t)
  #abline(v = mean(q$sr))
  #abline(v = mean(q$sr) + sd(q$sr))
  #abline(v = mean(q$sr) - sd(q$sr))
  
  return(q)
}

replace_df_tp <- function(df,test,r){
  if(nrow(df[df$nodeTransplantationPoint == test,]) > 0) {
    df[df$nodeTransplantationPoint == test,]$nodeTransplantationPoint <- r
  }
  return(df)
}
replace_df_tr <- function(df,test,r){
  if(nrow(df[df$nodeTransplant == test,]) > 0) {
    df[df$nodeTransplant == test,]$nodeTransplant <- r
  }
  return(df)
}

replace_df <- function(df,test,r){
  if(nrow(df[df$nodeTransplant == test,]) > 0) {
    df[df$nodeTransplant == test,]$nodeTransplant <- r
  }
  if(nrow(df[df$nodeTransplantationPoint == test,]) > 0) {
    df[df$nodeTransplantationPoint == test,]$nodeTransplantationPoint <- r
  }
  return(df)
}

cleanTP <- function(data) {
  res <- data
  if(nrow(res[is.na(res$nodeTransplant),]) > 0) {
    res[is.na(res$nodeTransplant),]$nodeTransplant <- "NA"
  }
  res <- replace_df(res,"CtDoImpl","Loop")
  res <- replace_df(res,"CtDoImpl","Loop")
  res <- replace_df(res,"CtForEachImpl","Loop")
  res <- replace_df(res,"CtForImpl","Loop")
  res <- replace_df(res,"CtWhileImpl","Loop")
  
  res <- replace_df(res,"CtInvocationImpl","Invocation")
  res <- replace_df(res,"CtSwitchImpl","Switch")
  res <- replace_df(res,"CtTryImpl","Try")
 
  res <- replace_df(res,"CtIfImpl","If")
  res <- replace_df(res,"CtReturnImpl","Return")
  res <- replace_df(res,"CtSynchronizedImpl","Synchronized")
  res <- replace_df(res,"CtThrowImpl","Throw")

  #res <- replace_df(res,"CtLocalVariableImpl","LocalVariable")
  res <- replace_df(res,"CtLocalVariableImpl","Assignement")
  res <- replace_df(res,"CtOperatorAssignmentImpl","Assignement")
  res <- replace_df(res,"CtAssignmentImpl","Assignement")

  res <- replace_df(res,"CtUnaryOperatorImpl","UnaryOperator")
  
  res <- replace_df(res,"CtBreakImpl","Break")
  res <- replace_df(res,"CtContinueImpl","Continue")
  res <- replace_df(res,"CtAssertImpl","Assert")
  return(res)
}


commons_codec_trials_2 <- cleanTP(commons_codec_trials)
commons_collections_trials_2 <- cleanTP(commons_collections_trials)
commons_io_trials_2 <- cleanTP(commons_io_trials)
commons_lang_trials_2 <- cleanTP(commons_lang_trials)
gson_trials_2 <- cleanTP(gson_trials)
jgit_trials_2 <- cleanTP(jgit_trials)
all_trials_2 <- cleanTP(all_trials)
#commons_codec_trials_2$nodeTransplantationPoint = 

q <- transfoBarPlot_tp(all_trials_2, 1, "all")
q1 <- transfoBarPlot_tp(commons_codec_trials_2, 50, "commons_codec")
q2 <- transfoBarPlot_tp(commons_collections_trials_2, 50, "commons_collections")
q3 <- transfoBarPlot_tp(commons_io_trials_2, 50, "commons_io")
q4 <- transfoBarPlot_tp(commons_lang_trials_2, 50, "commons_lang")
q5 <- transfoBarPlot_tp(gson_trials_2, 50, "gson")
q6 <- transfoBarPlot_tp(jgit_trials_2, 50, "jgit")



transfoBarPlot_tr <- function(data, filter_val,t) {
  all_success <- data %>% filter(status >= 0 & name=="add") %>% group_by(nodeTransplant) %>% count_()
  all_compile <- data %>% filter(status >= -1 & name=="add") %>% group_by(nodeTransplant) %>% count_()
  
  r <- merge(all_success,all_compile, by='nodeTransplant', all=T) 
  if(nrow(r[is.na(r$'n.x'),]) > 0) {
      r[is.na(r$'n.x'),]$'n.x' <- 0
    }
  r$sr <- r$'n.x' / r$'n.y'
  q <- r %>% filter(n.y > filter_val)
  weightedMedian(q$sr, q$n.y)
  weightedMean(q$sr, q$n.y)
  median(q$sr)
  mean(q$sr)
  sd(q$sr)
  par(mar = c(4, 16, 0, 0)) 
  
  barplot(q$sr,names.arg = q$nodeTransplant, las = 2, horiz = T, col=c("darkblue"), border = T, main = t)
  abline(v = mean(q$sr))
  #abline(v = mean(q$sr) + sd(q$sr))
  #abline(v = mean(q$sr) - sd(q$sr))
  return(q)
}

limit_val <- 25

q <- transfoBarPlot_tr(all_trials_2, 50, "all")
q_add_all <- transfoBarPlot_tr(all_trials_2, limit_val, "all")
q_add_all_uf <- transfoBarPlot_tr(all_trials_2, 0, "all")
q1 <- transfoBarPlot_tr(commons_codec_trials_2, limit_val, "commons_codec")
q2 <- transfoBarPlot_tr(commons_collections_trials_2, limit_val, "commons_collections")
q3 <- transfoBarPlot_tr(commons_io_trials_2, limit_val, "commons_io")
q4 <- transfoBarPlot_tr(commons_lang_trials_2, limit_val, "commons_lang")
q5 <- transfoBarPlot_tr(gson_trials_2, limit_val, "gson")
q6 <- transfoBarPlot_tr(jgit_trials_2, limit_val, "jgit")
```

Plot add variant success rate in function of Transplant Type.

```{r add}

multiBarPlot_tr <- function(d1,d2,d3,d4,d5,d6,d) {
  q_tmp <- data.frame(d1$nodeTransplant, d1$sr, "commons-codec")
  yaq <- q_tmp
  colnames(yaq) <- c("nodeTransplant","SR","projet")
  
  q_tmp <- data.frame(d2$nodeTransplant, d2$sr, "commons-collections")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d3$nodeTransplant, d3$sr, "commons-io")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d4$nodeTransplant, d4$sr, "commons-lang")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d5$nodeTransplant, d5$sr, "gson")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d6$nodeTransplant, d6$sr, "jgit")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d$nodeTransplant, d$sr, "average")
  colnames(q_tmp) <- c("nodeTransplant","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  #yaq <- yaq %>% filter(nodeTransplant != "UnaryOperator")
  #yaq <- yaq %>% filter(nodeTransplant != "Break")
  #yaq <- yaq %>% filter(nodeTransplant != "Continue")
  #yaq <- yaq %>% filter(nodeTransplant != "Try")
  yaq <- yaq %>% filter(nodeTransplant != "Assert")
  #colnames(yaq) <- c("nodeTransplant","Success Rate","projet")
  
  # scale_fill_grey(start = 0.8, end = 0)+ theme_bw() +
  ggplot(data=yaq, aes(x=nodeTransplant, y=SR, fill=projet)) +
  geom_bar(stat="identity", position=position_dodge()) +
    theme(legend.position="bottom", legend.title = element_blank()) +
    xlab(label = "Transplant Node Type") +
    ylab(label = "ADD Neutral Variant Rate")
}


setEPS()
postscript("add-color.eps")
multiBarPlot_tr(q1,q2,q3,q4,q5,q6,q)

dev.off()

```

## Delete

Clean up and regrouping data.

```{r pre_delete}
transfoBarPlot_del <- function(data, filter_val,t) {
  all_success <- data %>% filter(status >= 0 & name=="delete") %>% group_by(nodeTransplantationPoint) %>% count_()
  all_compile <- data %>% filter(status >= -1 & name=="delete") %>% group_by(nodeTransplantationPoint) %>% count_()
  
  r <- merge(all_success,all_compile, by='nodeTransplantationPoint', all=T) 
  r[is.na(r$'n.x'),]$'n.x' <- 0
  r$sr <- r$'n.x' / r$'n.y'
  
  q <- r %>% filter(n.y > filter_val)
  weightedMedian(q$sr, q$n.y)
  weightedMean(q$sr, q$n.y)
  median(q$sr)
  mean(q$sr)
  sd(q$sr)
  par(mar = c(4, 16, 0, 0)) 
  
  barplot(q$sr,names.arg = q$nodeTransplantationPoint, las = 2, horiz = T, col=c("darkblue"), border = T, main = t)
  abline(v = mean(q$sr))
  #abline(v = mean(q$sr) + sd(q$sr))
  #abline(v = mean(q$sr) - sd(q$sr))
  return(q)
}


q <- transfoBarPlot_del(all_trials_2, 100, "all")
q_del_all <- transfoBarPlot_del(all_trials_2, 25, "all")
q1 <- transfoBarPlot_del(commons_codec_trials_2, 25, "commons_codec")
q2 <- transfoBarPlot_del(commons_collections_trials_2, 25, "commons_collections")
q3 <- transfoBarPlot_del(commons_io_trials_2, 25, "commons_io")
q4 <- transfoBarPlot_del(commons_lang_trials_2, 25, "commons_lang")
q5 <- transfoBarPlot_del(gson_trials_2, 25, "gson")
q6 <- transfoBarPlot_del(jgit_trials_2, 25, "jgit")
```
Plot delete variant success rate in function of Transplantation point Type.
```{r del_ya2}
multiBarPlot_del_tp <- function(d1,d2,d3,d4,d5,d6,d) {
  q_tmp <- data.frame(d1$nodeTransplantationPoint, d1$sr, "commons-codec")
  yaq <- q_tmp
  colnames(yaq) <- c("nodeTransplantationPoint","SR","projet")
  
  q_tmp <- data.frame(d2$nodeTransplantationPoint, d2$sr, "commons-collections")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d3$nodeTransplantationPoint, d3$sr, "commons-io")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d4$nodeTransplantationPoint, d4$sr, "commons-lang")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d5$nodeTransplantationPoint, d5$sr, "gson")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d6$nodeTransplantationPoint, d6$sr, "jgit")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  q_tmp <- data.frame(d$nodeTransplantationPoint, d$sr, "average")
  colnames(q_tmp) <- c("nodeTransplantationPoint","SR","projet")
  yaq <- rbind(yaq, q_tmp)
  
  yaq <- yaq %>% filter(nodeTransplantationPoint != "UnaryOperator")
  yaq <- yaq %>% filter(nodeTransplantationPoint != "Break")
  yaq <- yaq %>% filter(nodeTransplantationPoint != "Continue")
  yaq <- yaq %>% filter(nodeTransplantationPoint != "Try")
  yaq <- yaq %>% filter(nodeTransplantationPoint != "Switch")
  
  # scale_fill_grey(start = 0.8, end = 0)+ theme_bw() +
  
  ggplot(data=yaq, aes(x=nodeTransplantationPoint, y=SR, fill=projet)) +
  geom_bar(stat="identity", position=position_dodge()) + 
    theme(legend.position="bottom", legend.title = element_blank()) +
    xlab(label = "Location Node Type") +
    ylab(label = "DELETE Neutral Variant Rate")
}


setEPS()
postscript("delete-color.eps")
multiBarPlot_del_tp(q1,q2,q3,q4,q5,q6,q)

dev.off()
```

## Replace

Plot replace variant success rate in function of Transplantation point Type.

```{r replace}

transfoBarPlot_rep_tp <- function(data, filter_val,t) {
  all_success <- data %>% filter(status >= 0 & name=="replace") %>% group_by(nodeTransplantationPoint) %>% count_()
  all_compile <- data %>% filter(status >= -1 & name=="replace") %>% group_by(nodeTransplantationPoint) %>% count_()
  
  r <- merge(all_success,all_compile, by='nodeTransplantationPoint', all=T) 
  #r[is.na(r$'n.x'),]$'n.x' <- 0
  r$sr <- r$'n.x' / r$'n.y'
  
  q <- r %>% filter(n.y > filter_val)
  weightedMedian(q$sr, q$n.y)
  weightedMean(q$sr, q$n.y)
  median(q$sr)
  mean(q$sr)
  sd(q$sr)
  par(mar = c(4, 16, 0, 0)) 
  
  barplot(q$sr,names.arg = q$nodeTransplantationPoint, las = 2, horiz = T, col=c("darkblue"), border = T, main = t)
  abline(v = mean(q$sr))
 return(q)
}
#abline(v = mean(q$sr))
#abline(v = mean(q$sr) + sd(q$sr))
#abline(v = mean(q$sr) - sd(q$sr))

q <- transfoBarPlot_rep_tp(all_trials_2, 500, "all")
q_rep_all_uf <- transfoBarPlot_rep_tp(all_trials_2, 0, "all")
q1 <- transfoBarPlot_rep_tp(commons_codec_trials_2, 50, "commons_codec")
q2 <- transfoBarPlot_rep_tp(commons_collections_trials_2, 50, "commons_collections")
q3 <- transfoBarPlot_rep_tp(commons_io_trials_2, 50, "commons_io")
q4 <- transfoBarPlot_rep_tp(commons_lang_trials_2, 50, "commons_lang")
q5 <- transfoBarPlot_rep_tp(gson_trials_2, 50, "gson")
q6 <- transfoBarPlot_rep_tp(jgit_trials_2, 50, "jgit")

```

Plot replace variant success rate in function of Transplant Type.

```{r replace_2}

transfoBarPlot_rep_tr <- function(data, filter_val,t) {
  all_success <- data %>% filter(status >= 0 & name=="replace") %>% group_by(nodeTransplant) %>% count_()
  all_compile <- data %>% filter(status >= -1 & name=="replace") %>% group_by(nodeTransplant) %>% count_()
  
  r <- merge(all_success,all_compile, by='nodeTransplant', all=T) 
  if(nrow(r[is.na(r$'n.x'),]) > 0) {
      r[is.na(r$'n.x'),]$'n.x' <- 0
    }
  r$sr <- r$'n.x' / r$'n.y'
  
  q <- r %>% filter(n.y > filter_val)
  weightedMedian(q$sr, q$n.y)
  weightedMean(q$sr, q$n.y)
  median(q$sr)
  mean(q$sr)
  sd(q$sr)
  par(mar = c(4, 16, 0, 0)) 
  
  barplot(q$sr,names.arg = q$nodeTransplant, las = 2, horiz = T, col=c("darkblue"), border = T, main = t)
  abline(v = mean(q$sr))
  #abline(v = mean(q$sr) + sd(q$sr))
  #abline(v = mean(q$sr) - sd(q$sr))
  return(q)
}

q <- transfoBarPlot_rep_tr(all_trials_2, 500, "all")
q1 <- transfoBarPlot_rep_tr(commons_codec_trials_2, 50, "commons_codec")
q2 <- transfoBarPlot_rep_tr(commons_collections_trials_2, 50, "commons_collections")
q3 <- transfoBarPlot_rep_tr(commons_io_trials_2, 50, "commons_io")
q4 <- transfoBarPlot_rep_tr(commons_lang_trials_2, 50, "commons_lang")
q5 <- transfoBarPlot_rep_tr(gson_trials_2, 50, "gson")
q6 <- transfoBarPlot_rep_tr(jgit_trials_2, 50, "jgit")

```